Random Forest in R example with IRIS Data
========================================================


#Random Forest in R example IRIS data


#Split iris data to Training data and testing data

```{r}
ind <- sample(2,nrow(iris),replace=TRUE,prob=c(0.7,0.3))
trainData <- iris[ind==1,]
testData <- iris[ind==2,]
```
#Load Library Random FOrest
```{r}
library(randomForest)
```
#Generate Random Forest learning treee
```{r}
iris_rf <- randomForest(Species~.,data=trainData,ntree=100,proximity=TRUE)
table(predict(iris_rf),trainData$Species)
```

Try to print Random Forest model and see the importance features
```{r}
print(iris_rf)
plot(iris_rf)
importance(iris_rf)
varImpPlot(iris_rf)
```

#Try to build random forest for testing data
```{r}
irisPred<-predict(iris_rf,newdata=testData)
table(irisPred, testData$Species)
```
Try to see the margin, positive or negative, if positif it means correct classification
```{r}
plot(margin(iris_rf,testData$Species))
```

Try to tune Random Forest
```{r}

tune.rf <- tuneRF(iris[,-5],iris[,5], stepFactor=0.5)
print(tune.rf)
```