SVM example with Iris Data in R
========================================================

Use library e1071, you can install it using install.packages("e1071").
Load library 

```{r}
library("e1071")
```

Using Iris data
```{r}
head(iris,5)
```

Attach the Data
```{r}
attach(iris)
```

Divide Iris data to x (containt the all features) and y only the classes
```{r}
x <- subset(iris, select=-Species)
y <- Species
```

Create SVM Model and show summary 

```{r}
svm_model <- svm(Species ~ ., data=iris)
summary(svm_model)
```


Or you can use command like this 

Create SVM Model and show summary 

```{r}
svm_model1 <- svm(x,y)
summary(svm_model1)
```



Run Prediction and you can measuring the execution time in R



```{r}
pred <- predict(svm_model1,x)
system.time(pred <- predict(svm_model1,x))

```

See the confusion matrix result of prediction, using command table to compare the result of SVM prediction and the class data in y variable.
```{r}
table(pred,y)

```

TUning SVM to find the best cost and gamma ..

```{r}
svm_tune <- tune(svm, train.x=x, train.y=y, 
              kernel="radial", ranges=list(cost=10^(-1:2), gamma=c(.5,1,2)))

print(svm_tune)
```

After you find the best cost and gamma, you can create svm model again and try to run again
```{r}
svm_model_after_tune <- svm(Species ~ ., data=iris, kernel="radial", cost=1, gamma=0.5)
summary(svm_model_after_tune)

```

Run Prediction again with new model



```{r}
pred <- predict(svm_model_after_tune,x)
system.time(predict(svm_model_after_tune,x))

```

See the confusion matrix result of prediction, using command table to compare the result of SVM prediction and the class data in y variable.
```{r}
table(pred,y)

```
